\section{Introduction}
The online gaming community always had its fair share of scandals and controversies.
One main example of that was the \textbf{\emph{\#GamerGate}} controversy which started as an harassment campaign against several women in the gaming industry and then backfired as the hash-tag was used against the entire online gaming community which was accused as being sexist, racist and violent. These events raised some concerns regarding verbal violence in gaming communities and their usage of offensive language, coming from that, the following questions were the base of our research:

\begin{itemize}
    \item What is the attitude of gaming communities to women? How sexist are those communities?
    \item Are the communities racist?
    \item Do they engage in politics? What is their relation towards Trump?
\end{itemize}  

We set-out to try and answer these questions in an objective and empirical manner. For that, we collected data from Twitter and Reddit, the data collected per game from each of the platforms, we then analyzed the data for each game separately applying various NLP models to try and evaluate the different gaming communities linguistic properties in respect to our research question.
We wanted to compare between the communities and to get an empirical rating for each communities sexism, racism and Trump hate and therefore we invented our novel \emph{ negativity evaluation metric - NEM}.

Our entire project code could be found in our GitHub repository \href{https://github.com/goldmyu/games-social-nets}{games-social-nets}.
